Placeholder

### 2021-02-22 Paper_Histograms.Rmd
Moved EDGI participants to the NBR cohort rather than GLAD

GLAD.prepan <- dat.prepan %>%
  filter(Sample == "GLAD" | 
           Sample == "EDGI")

NBR.prepan <- dat.prepan %>%
  filter(Sample == "NBR")

@@

### retro
GLAD.retro <- dat.retro %>%
  filter(Sample == "GLAD" | 
           Sample == "EDGI")

NBR.retro <- dat.retro %>%
  filter(Sample == "NBR")

@@

dat.retro <- dat.retro %>% 
  mutate(Sample_plot = 
           case_when(
             dat.retro$Sample == "GLAD" ~ "GLAD/EDGI",
             dat.retro$Sample == "EDGI" ~ "GLAD/EDGI",
             dat.retro$Sample == "NBR" ~ "NBR",
             dat.retro$Sample == "RAMP" ~ "RAMP"
           ))

>>>>

GLAD.prepan <- dat.prepan %>%
  filter(Sample == "GLAD")

NBR.prepan <- dat.prepan %>%
  filter(Sample == "NBR" | 
           Sample == "EDGI")

@@

### retro
GLAD.retro <- dat.retro %>%
  filter(Sample == "GLAD")

NBR.retro <- dat.retro %>%
  filter(Sample == "NBR" | 
           Sample == "EDGI")

@@

dat.retro <- dat.retro %>% 
  mutate(Sample_plot = 
           case_when(
             dat.retro$Sample == "GLAD" ~ "GLAD/EDGI",
             dat.retro$Sample == "EDGI" ~ "NBR",
             dat.retro$Sample == "NBR" ~ "NBR",
             dat.retro$Sample == "RAMP" ~ "RAMP"
           ))
